TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-02-25 article.tex
TTT: illustrations, toqué el final

h = History(composition=composition, times = times, sigma = 2.0, gamma = 0.02)
convergence(h,epsilon=0.01, iterations=10)
\end{lstlisting}

\begin{figure}[h]
    \centering
    \includegraphics[page={1},width=.6\linewidth]{figures/atp}
    \caption{
    }
    \caption{ATP}
    \label{fig:atp}
\end{figure}

@@

\newpage
\section{Models and software}

@@

\newpage
\section{Appendix} \label{app:technical}
% Appendices can be included after the bibliography (with a page break). Each
% section within the appendix should have a proper section title (rather than
% just \emph{Appendix}).

>>>>

h = History(composition=composition, times = times, sigma = 2.0, gamma = 0.02)
convergence(h,epsilon=0.01, iterations=10)
\end{lstlisting}
%
\en{In this code we open the file \texttt{atp.csv}, create the variables \texttt{times} and \texttt{composition}, and instantiate the class \texttt{History}.}
\es{En este código abrimos el archivo \texttt{csv}, creamos las variables \texttt{times} y \texttt{composition} e instanciamos la clase \texttt{History}.}
%
\en{Times are defined as days elapsed from a base date (any date) to the tournament start time.}
\es{Los tiempos los definimos como días transcurridos desde una fecha base (cualquiera sea) hasta el inicio del toreno.}
%
\en{We subtract the number of rounds to roughly differentiate the days within each tournament, but this is not necessary.}
\es{Restamos el número de ronda para diferenciar aproximadamente los días al interior de cada torneo, pero no es algo que sea necesario.}
%
\en{The composition of the events depends on whether the games were doubles or singles.}
\es{La composición de los eventos dependen de si la partidas fueron dobles o singles.}
%
\en{The results are implied by the order in which we set the composition, always placing the winning team first.}
\es{Los resultados quedan implicitos por el orden en que armamos la composición, poniendo siempre primero al equipo ganador.}
%
\en{When initializing the class \texttt{History} we also modify the default values of \texttt{sigma} and \texttt{gamma}.}
\es{Al inicializar la clase \texttt{History} modificamos los valores por defecto de \texttt{sigma} y \texttt{gamma}.}
%
\en{Finally, we converge the history to obtain TrueSkill Through Time estimates, explicitly indicating the breaking criterion: when the change between iterations is less than $0.01$, or when $10$ iterations are reached.}
\es{Finalmente, convergemos la historia para obtener las estimaciones de TrueSkill Through Time, indicando explícitamente el criterio de corte: cuando la modificación entrte iteraciones sea menor a $0.01$, o cuando se alcanzan las $10$ iteraciones.}
%
\en{The learning curves are obtained in the same way as we have seen before.}
\es{Las curvas de aprendizaje se obtienen de la misma forma que hemos visto.}
%
\en{In the following figure we plot the learning curves of 8 important players in the history of the ATP.}
\es{En la siguiente figura graficamos las curvas de aprendizaje de 8 jugadores importantes de la historia de la ATP.}
%
\begin{figure}[h]
    \centering
    \includegraphics[page={1},width=.6\linewidth]{figures/atp}
    \caption{ATP}
    \label{fig:atp}
\end{figure}

@@

\section{Models and software}

@@

\newpage
\section{Appendix} \label{app:technical}

\todo[inline]{Código de Julia y R}

\todo[inline]{Código de Python y R}

% Appendices can be included after the bibliography (with a page break). Each
% section within the appendix should have a proper section title (rather than
% just \emph{Appendix}).
